---
title: "Housing Permit Data Summary: MO3"
author: Ryan Hafen
output:
  packagedocs:
    toc: true
    css: menu-fix.css
navpills: |
  <li class=''><a href="index.html">All Datasets</a></li>
  <li role="presentation" class="dropdown active">
  <a id="study-drop" href="#" class="dropdown-toggle" data-toggle="dropdown" aria-haspopup="true" role="button" aria-expanded="false">Dataset (MO3)<span class="caret"></span></a>
  <ul id="menu1" class="dropdown-menu dropdown-menu-right" role="menu" aria-labelledby="study-drop">
  <li class=''><a href='BOS1.html'>BOS1</a></li>
  <li class=''><a href='BOS2.html'>BOS2</a></li>
  <li class=''><a href='CHI1.html'>CHI1</a></li>
  <li class=''><a href='ED1.html'>ED1</a></li>
  <li class=''><a href='ED2.html'>ED2</a></li>
  <li class=''><a href='IL1.html'>IL1</a></li>
  <li class=''><a href='IL2.html'>IL2</a></li>
  <li class=''><a href='MD1.html'>MD1</a></li>
  <li class=''><a href='MD2.html'>MD2</a></li>
  <li class=''><a href='MD3.html'>MD3</a></li>
  <li class=''><a href='MD4.html'>MD4</a></li>
  <li class=''><a href='MD5.html'>MD5</a></li>
  <li class=''><a href='MD6.html'>MD6</a></li>
  <li class=''><a href='MO1.html'>MO1</a></li>
  <li class=''><a href='MO2.html'>MO2</a></li>
  <li class='active'><a href='MO3.html'>MO3</a></li>
  <li class=''><a href='MO4.html'>MO4</a></li>
  <li class=''><a href='MO5.html'>MO5</a></li>
  <li class=''><a href='MO6.html'>MO6</a></li>
  <li class=''><a href='MO7.html'>MO7</a></li>
  <li class=''><a href='NO1.html'>NO1</a></li>
  <li class=''><a href='NO2.html'>NO2</a></li>
  <li class=''><a href='NYC2.html'>NYC2</a></li>
  <li class=''><a href='SEA1.html'>SEA1</a></li>
  <li class=''><a href='SEA2.html'>SEA2</a></li>
  <li class=''><a href='WA.html'>WA</a></li>
  </ul>
  </li>
---


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(rbokeh)
library(knitr)
load("/var/folders/n4/6ztyqms165s3r_4n001n1y6m0000gn/T//RtmpvNpZPH/file421bb1153f5")
```


```{r echo=FALSE, results='asis'}
if(!is.null(di$meta)) {
  nms <- names(di$meta)
  tmpdf <- data.frame(
    v1 = gsub("_", " ", nms),
    v2 = unname(unlist(di$meta)))

  txt <- c("# Meta #", "",
    "|  property  |  value  |",
    "| ---------- | ------- |",
    apply(tmpdf, 1, function(x) {
      paste("|", paste(x, collapse = " | "), "|")}))

  cat(paste(txt, collapse = "\n"))
}
```

# Sample #

```{r echo=FALSE}
di$head
```

# Missing Values #

```{r echo=FALSE, message=FALSE}
plot_missing(di)
```

# Variables #

<!--

```{r echo=FALSE, results='asis'}
vartab <- data.frame(variable = names(di$var_summ), type = unname(sapply(di$var_summ, function(x) x$type)))
knitr::kable(vartab)
```
-->

```{r echo=FALSE, results='asis'}
txt <- ""
if(length(di$na_cols) > 0)
 txt <- c(paste0("The following variables are all NA: `",
  paste0(names(di$na_cols), collapse = "`, `"), "`"), "")

if(length(di$dups) > 0) {
  txt <- c(txt, "The following variables are duplicates:", "",
    sapply(di$dups, function(x) {
      paste0("- `", paste0(x, collapse = "`, `"), "`")
    }), "")

cat(paste(txt, collapse = "\n"))
}
```

## council_district ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["council_district"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## permit_value ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["permit_value"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## school_district ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["school_district"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## number ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["number"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## month ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["month"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## county ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["county"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## prefix ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["prefix"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## year ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["year"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## dwelling_units_gained_or_lost ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["dwelling_units_gained_or_lost"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## suffix ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["suffix"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## pin ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["pin"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## res_non ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["res_non"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## fraction ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["fraction"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## structure_class ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["structure_class"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## how_far_north ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["how_far_north"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## type ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["type"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## sf_mf ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["sf_mf"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## project_description ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["project_description"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## parcel ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["parcel"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## applicant_representative ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["applicant_representative"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## day ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["day"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## applicant_name ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["applicant_name"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## legal_description ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["legal_description"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## class_description ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["class_description"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## subdivision ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["subdivision"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## name ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["name"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## how_far_east ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["how_far_east"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## permit_number ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["permit_number"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```



## location_1.human_address ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["location_1.human_address"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```





## location_2.human_address ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["location_2.human_address"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```


