---
title: "Housing Permit Data Summary: NO1"
author: Ryan Hafen
output:
  packagedocs:
    toc: true
    css: menu-fix.css
navpills: |
  <li class=''><a href="index.html">All Datasets</a></li>
  <li role="presentation" class="dropdown active">
  <a id="study-drop" href="#" class="dropdown-toggle" data-toggle="dropdown" aria-haspopup="true" role="button" aria-expanded="false">Dataset (NO1)<span class="caret"></span></a>
  <ul id="menu1" class="dropdown-menu dropdown-menu-right" role="menu" aria-labelledby="study-drop">
  <li class=''><a href='BOS1.html'>BOS1</a></li>
  <li class=''><a href='BOS2.html'>BOS2</a></li>
  <li class=''><a href='CHI1.html'>CHI1</a></li>
  <li class=''><a href='ED1.html'>ED1</a></li>
  <li class=''><a href='ED2.html'>ED2</a></li>
  <li class=''><a href='IL1.html'>IL1</a></li>
  <li class=''><a href='IL2.html'>IL2</a></li>
  <li class=''><a href='MD1.html'>MD1</a></li>
  <li class=''><a href='MD2.html'>MD2</a></li>
  <li class=''><a href='MD3.html'>MD3</a></li>
  <li class=''><a href='MD4.html'>MD4</a></li>
  <li class=''><a href='MD5.html'>MD5</a></li>
  <li class=''><a href='MD6.html'>MD6</a></li>
  <li class=''><a href='MO1.html'>MO1</a></li>
  <li class=''><a href='MO2.html'>MO2</a></li>
  <li class=''><a href='MO3.html'>MO3</a></li>
  <li class=''><a href='MO4.html'>MO4</a></li>
  <li class=''><a href='MO5.html'>MO5</a></li>
  <li class=''><a href='MO6.html'>MO6</a></li>
  <li class=''><a href='MO7.html'>MO7</a></li>
  <li class='active'><a href='NO1.html'>NO1</a></li>
  <li class=''><a href='NO2.html'>NO2</a></li>
  <li class=''><a href='NYC2.html'>NYC2</a></li>
  <li class=''><a href='SEA1.html'>SEA1</a></li>
  <li class=''><a href='SEA2.html'>SEA2</a></li>
  <li class=''><a href='WA.html'>WA</a></li>
  </ul>
  </li>
---


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(rbokeh)
library(knitr)
load("/var/folders/n4/6ztyqms165s3r_4n001n1y6m0000gn/T//RtmpvNpZPH/file421b73b42a7e")
```


```{r echo=FALSE, results='asis'}
if(!is.null(di$meta)) {
  nms <- names(di$meta)
  tmpdf <- data.frame(
    v1 = gsub("_", " ", nms),
    v2 = unname(unlist(di$meta)))

  txt <- c("# Meta #", "",
    "|  property  |  value  |",
    "| ---------- | ------- |",
    apply(tmpdf, 1, function(x) {
      paste("|", paste(x, collapse = " | "), "|")}))

  cat(paste(txt, collapse = "\n"))
}
```

# Sample #

```{r echo=FALSE}
di$head
```

# Missing Values #

```{r echo=FALSE, message=FALSE}
plot_missing(di)
```

# Variables #

<!--

```{r echo=FALSE, results='asis'}
vartab <- data.frame(variable = names(di$var_summ), type = unname(sapply(di$var_summ, function(x) x$type)))
knitr::kable(vartab)
```
-->

```{r echo=FALSE, results='asis'}
txt <- ""
if(length(di$na_cols) > 0)
 txt <- c(paste0("The following variables are all NA: `",
  paste0(names(di$na_cols), collapse = "`, `"), "`"), "")

if(length(di$dups) > 0) {
  txt <- c(txt, "The following variables are duplicates:", "",
    sapply(di$dups, function(x) {
      paste0("- `", paste0(x, collapse = "`, `"), "`")
    }), "")

cat(paste(txt, collapse = "\n"))
}
```

## propertykey ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["propertykey"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## matchaddress ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["matchaddress"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## planningdist ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["planningdist"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## streetsuffix ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["streetsuffix"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## streetdir ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["streetdir"]]
vr$artifacts$fg
```

### Frequency table ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## permitnumber ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["permitnumber"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## issuedate ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["issuedate"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## housenum ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["housenum"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## applicationdate ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["applicationdate"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## streetname ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["streetname"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## description ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["description"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## zoning ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["zoning"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## parcelowner ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["parcelowner"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## unitnumber ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["unitnumber"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## y ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["y"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## x ##

### Distribution ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["x"]]
vr$artifacts$fg
```

### Summary statistics ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```

## applicantname ##

### Distribution of top 50 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr <- di$var_summ[["applicantname"]]
vr$artifacts$fg
```

### Frequency table of top 100 variables ###

```{r, echo=FALSE, message=FALSE, results='asis'}
vr$artifacts$tb
```
